Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2014-10-08 Report/joint_wsrm_formulation.tex
updated document with thanks and punctuations

The \ac{Q-WSRM} formulation extends the \emph{backpressure algorithm} to the \ac{MIMO}-\ac{OFDM} downlink framework, in which the multiple \acp{BS} act as the source nodes and the user terminals as the receiver nodes. The control policy in the form of transmit precoders is designed to minimize the number of queued packets waiting at the \acp{BS}. In order to find the optimal algorithm, we use the Lyapunov function which is predominantly used in the control theory for the system stability. Since at each time slot, the system can be described by the channel conditions and the number of backlogged packets of each user, the Lyapunov function is used to provide a scalar measure, which grows large when the system moves toward the undesirable state. Following the approach in \cite{neely2010stochastic}, the scalar measure for the queue stability is given by
\begin{equation}
\mathrm{L}\sset{\mbf{Q}(i)} = \frac{1}{2} \, \sum_{k \in \mc{U}} Q_k^2(i),
\end{equation}
where \me{\mbf{Q}(i)} denotes the stacked user queues at the \me{\ith{i}} slot and \me{\frac{1}{2}} is used for the convenience. The Lyapunov function provides a measure of congestion in the system, as discussed in \cite[Ch. 3]{neely2010stochastic}. The Lyapunov function drift, expressed as \me{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)}}, is given by 
\begin{IEEEeqnarray}{rCl}\label{eqn-3.1}
&=&\frac{1}{2} \Big [ \sum_{k \in \mc{U}} \, \Big ( \left [ Q_k(i) - t_k(i) \right ]^+ + \lambda_k(i) \Big )^2 - Q^2_k(i) \Big ] \IEEEyessubnumber \label{eqn-3.1.0} \\
&\leq& \sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} + \sum_{k \in \mc{U}} Q_k(i) \set{ \lambda_k(i) - t_k(i) }, \IEEEyessubnumber \label{drift-exp}
\end{IEEEeqnarray}
where the inequality is due to the upper bound
\begin{equation}
\sset{\max(Q-t,0) + \lambda)}^2 \leq Q^2 + t^2 + \lambda^2 + 2 Q (\lambda - t).
\end{equation}
The total number of backlogged packets at any given instant \me{i} is reduced by minimizing the conditional expectation of the Lyapunov drift expression \eqref{drift-exp} given the current number of queued packets \me{\mbfa{Q}(i)} waiting in the system. The expectation is taken over all possible arrival and transmission rates of the users to obtain the optimal rate allocation strategy.

Now, the conditional Lyapunov drift, denoted by \me{\Delta{(\mbfa{Q}(i))}}, is given by the infimum over the transmission rate as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{rCl} \label{backpressure-approx}
	\underset{\mbf{t}}{\text{inf}} && \Delta(\mbf{Q}(i)) \triangleq \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
	&\leq& \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)}}_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)}, \eqsub \label{backpressure-approx-1b}
\end{IEEEeqnarray}}{
{\allowdisplaybreaks
\begin{IEEEeqnarray}{CL} \label{backpressure-approx}
	\underset{\mbf{t}}{\text{inf}} \quad & \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
	\leq & \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \Big \lbrace \sum_{k \in \mc{U}} \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i) \Big \rbrace }_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) \nonumber \\
	& \qquad \qquad {} - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\Big \lbrace \sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i) \Big \rbrace, \eqsub \label{backpressure-approx-1b}
\end{IEEEeqnarray}}}
%\begin{figure*}
%\begin{IEEEeqnarray}{rCl} \label{backpressure-approx}
%	\underset{\mbf{t}}{\text{minimize}} &\quad& \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \vspace{-0.25in}\\
%	& \leq & \sum_{k \in \mc{U}} Q_k(i) A_k(i) - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)} + \overbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)}}^{\le B}\IEEEyessubnumber \label{backpreassure-approx-1b}
%\end{IEEEeqnarray}	
%\vspace{-0.25in}
%\end{figure*}
where the first term in \eqref{backpressure-approx-1b} follows from the Poisson arrival process. Since the transmission and the arrival rates are bounded, we can upper bound the second order moments in the first term of \eqref{backpressure-approx-1b} by a constant \me{B} that can be eliminated from the optimization problem \cite{neely2010stochastic}.

>>>>

The \ac{Q-WSRM} formulation extends the \emph{backpressure algorithm} to the downlink \ac{MIMO}-\ac{OFDM} framework, in which the multiple \acp{BS} act as the source nodes and the user terminals as the receiver nodes. The control policy in the form of transmit precoders aims at minimizing the number of queued packets waiting in the \acp{BS}. In order to find the optimal strategy, we resort to the Lyapunov theory, which is predominantly used in the control theory to achieve system stability. Since at each time slot, the system is described by the channel conditions and the number of backlogged packets of each user, the Lyapunov function is used to provide a scalar measure, which grows large when the system moves toward the undesirable state. Following similar approach as in \cite{neely2010stochastic}, the scalar measure for the queue stability is given by
\begin{equation}
\mathrm{L}\sset{\mbf{Q}(i)} = \frac{1}{2} \, \sum_{k \in \mc{U}} Q_k^2(i),
\end{equation}
where \me{\mbf{Q}(i)} denotes the stacked user queues at the \me{\ith{i}} slot and \me{\tfrac{1}{2}} is used for the convenience. It provides a scalar measure of congestion present in the system \cite[Ch. 3]{neely2010stochastic}.

The optimal transmission rate vector \me{\mbf{t}} to minimize the total number of backlogged packets in the system is obtained by minimizing the Lyapunov function drift expressed as
\iftoggle{single_column}{
\begin{multline}\label{eqn-3.1}
\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} = \frac{1}{2} \Big [ \sum_{k \in \mc{U}} \, \Big ( \left [ Q_k(i) - t_k(i) \right ]^+ + \lambda_k(i) \Big )^2 - Q^2_k(i) \Big ].
\end{multline}}{
\begin{multline}\label{eqn-3.1}
\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} = \\ \frac{1}{2} \Big [ \sum_{k \in \mc{U}} \, \Big ( \left [ Q_k(i) - t_k(i) \right ]^+ + \lambda_k(i) \Big )^2 - Q^2_k(i) \Big ].
\end{multline}}
In order to eliminate the nonlinear operator \me{[x]^+}, we bound the expression in \eqref{eqn-3.1} as
\begin{equation}
\leq \sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} + \sum_{k \in \mc{U}} Q_k(i) \set{ \lambda_k(i) - t_k(i) },
\label{drift-exp}
\end{equation}
by using the following inequality 
\begin{equation}
\sset{\max(Q-t,0) + \lambda)}^2 \leq Q^2 + t^2 + \lambda^2 + 2 Q (\lambda - t).
\end{equation}
The total number of backlogged packets at any given instant \me{i} is reduced by minimizing the conditional expectation of the Lyapunov drift expression \eqref{drift-exp} given the current number of queued packets \me{\mbfa{Q}(i)} waiting in the system. The expectation is taken over all possible arrival and transmission rates of the users to obtain the optimal rate allocation strategy.

Now, the conditional Lyapunov drift, denoted by \me{\Delta{(\mbfa{Q}(i))}}, is given by the infimum over the transmission rate as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{rCl} \label{backpressure-approx}
	\underset{\mbf{t}}{\text{inf}} && \Delta(\mbf{Q}(i)) \triangleq \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
	&\leq& \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)}}_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)}, \eqsub \label{backpressure-approx-1b}
\end{IEEEeqnarray}}{
\begin{IEEEeqnarray}{CL} \label{backpressure-approx}
	\underset{\mbf{t}}{\text{inf}} \quad & \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
	\leq & \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \Big \lbrace \sum_{k \in \mc{U}} \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i) \Big \rbrace }_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) \nonumber \\
	& \qquad \qquad {} - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\Big \lbrace \sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i) \Big \rbrace, \eqsub \label{backpressure-approx-1b}
\end{IEEEeqnarray}}
where the first term in \eqref{backpressure-approx-1b} follows from the Poisson arrival process. Since the transmission and the arrival rates are bounded, we can upper bound the second order moments in the first term of \eqref{backpressure-approx-1b} by a constant \me{B} that can be eliminated from the optimization problem \cite{neely2010stochastic}.

### 2014-10-08 Report/kkt_mse_approach.tex
updated_halfcooked
updated document with thanks and punctuations

With the assumption of either one of the above conditions to be true, the problem in \eqref{eqn-mse-2} can be written as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \epsilon_{l,k,n}, \mvec{W}{k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
\text{subject to} & \hspace{0.5cm} & \nonumber \\
\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \, \|\mvec{w}{l,k,n}\|^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,y,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
\sigma_{l,k,n} : & \hspace{0.5cm} & \log(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{kkt-mse-1.4}
\end{IEEEeqnarray}
}{
\begin{IEEEeqnarray}{Rl}\label{kkt-mse-1}
	\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \epsilon_{l,k,n}, \mvec{W}{k,n}}}{\text{minimize}} & \quad \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
	\text{subject to} & \nonumber \\
	\alpha_{l,k,n} : &  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \|\mvec{w}{l,k,n}\|^2 \nonumber \\
	& + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,y,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
	\sigma_{l,k,n} : &  \log_2(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2)\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.3} \\
	\delta_b : & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \eqspace \label{kkt-mse-1.4}
\end{IEEEeqnarray}
}
where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}.

@@

\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i-1)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i-1)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i-1)}\|^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\

@@

\mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6}

@@

}{
{\allowdisplaybreaks

@@

	& \qquad{} + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i-1)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\

@@

	& \qquad {} + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6}
\end{IEEEeqnarray}}
}
Since the dual variables \me{\alpha^{(i)}} and \me{\sigma^{(i)}} are interdependent in \eqref{kkt-mse-2.2}, one has to be fixed to optimize for the other. In this problem, we fix the dual variable \me{\alpha^{(i)}} to a fixed value as in \eqref{kkt-mse-4.1} to obtain the other variables in \eqref{kkt-mse-4}. At each iteration, the dual variable \me{\alpha^{(i)}} is updated linearly from the earlier value \me{\alpha^{(i-1)}} by a step size of \me{\rho \in [0,1]}. It can be seen that, when the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative thereby forcing the dual variable \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}}, which in turn reduce the transmit precoder weights in \eqref{kkt-mse-4.3}. This reduction in the precoder weights forces the allocated rate of the user \me{k} to reduce from the previous iteration as \me{t_k^{(i)} < t_k^{(i-1)}}.

>>>>

With the assumption of either one of the above conditions to be true, the problem in \eqref{eqn-mse-2} can be written as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \epsilon_{l,k,n}, \mvec{W}{k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
\text{subject to} & \hspace{0.5cm} & \nonumber \\
\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \, \|\mvec{w}{l,k,n}\|^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
\sigma_{l,k,n} : & \hspace{0.5cm} & \log(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
\end{IEEEeqnarray}
}{
\begin{IEEEeqnarray}{Rl}\label{kkt-mse-1}
	\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \epsilon_{l,k,n}, \mvec{W}{k,n}}}{\text{minimize}} & \quad \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
	\text{subject to} & \nonumber \\
	\alpha_{l,k,n} : &  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \|\mvec{w}{l,k,n}\|^2 \nonumber \\
	& + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
	\sigma_{l,k,n} : &  \log_2(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2)\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.3} \\
	\delta_b : & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \eqspace \label{kkt-mse-1.4}
\end{IEEEeqnarray}
}
where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}.

@@

\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i-1)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i-1)} \mvec{H}{b_y,k,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i-1)}\|^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\

@@

\mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)}. \IEEEyessubnumber \label{kkt-mse-4.6}

@@

}{{\allowdisplaybreaks

@@

	& \qquad{} + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i-1)} \mvec{H}{b_y,k,n} \mvec{m}{x,y,n}^{(i)} \right |^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\

@@

	& \qquad {} + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)}. \IEEEyessubnumber \label{kkt-mse-4.6}
\end{IEEEeqnarray}}}
Since the dual variables \me{\alpha^{(i)}} and \me{\sigma^{(i)}} are interdependent in \eqref{kkt-mse-4}, one has to be fixed to optimize for the other. In this problem, we fix the dual variable \me{\alpha^{(i)}} to a fixed value as in \eqref{kkt-mse-4.1} to obtain the other variables in \eqref{kkt-mse-4}. At each iteration, the dual variable \me{\alpha^{(i)}} is updated linearly from the earlier value \me{\alpha^{(i-1)}} by a step size of \me{\rho \in [0,1]}. It can be seen that, when the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative thereby forcing the dual variable \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}}, which in turn reduce the transmit precoder weights in \eqref{kkt-mse-4.3}. This reduction in the precoder weights forces the allocated rate of the user \me{k} to reduce from the previous iteration as \me{t_k^{(i)} < t_k^{(i-1)}}.
